Toronto Paramedic Services

### 2024-09-26 paper/paper.qmd
Rendered a pdf version of the paper with all visualizations done - now need to edit writing.

```{r}
#| echo: false 
#| message: false
#| label: fig-map
#| fig-cap: EMS Demand Across Toronto Forward Sortation Areas (Based on data from 2022)

@@

ggplot(merged_map_data) + 
  geom_sf(aes(fill = EMS_Demand_Driver)) +
  labs(title = "EMS Demand Drivers By Forward Sortation Area (FSA)",
         x = "Longitude", y="Latitude", 
       caption = "Data Source: Open Canada 2021 Census - Boundary Files & Toronto Paramedic Services") +
  theme_light() + theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_discrete(name = "EMS Demand Driver") +
  scale_fill_manual(values = c("lightblue"))

>>>>

```{r, results = 'hide'}
#| message: false
#| echo: false 
#| warning: false
#| label: fig-map
#| fig-cap: EMS Demand Across Toronto Forward Sortation Areas (Based on data from 2022)

@@

ggplot(merged_map_data) + 
  geom_sf(aes(fill = EMS_Demand_Driver)) +
  labs(title = "EMS Demand Drivers By Forward Sortation Area (FSA)",
         x = "Longitude", y="Latitude", 
       caption = "Data Source: Open Canada 2021 Census & Toronto Paramedic Services") +
  theme_light() + theme(plot.title = element_text(hjust = 0.3)) +
  scale_fill_discrete(name = "EMS Demand Driver") +
  scale_fill_manual(values = c("lightblue"))
